Sparse model

### 2020-04-01 analysis/sparse_model.Rmd
sparse model description

## Sparse model for expression and genotype
 $$Y = \tilde{X}\beta + G\theta + \epsilon$$
$Y$: quantitative traits, $N$ x 1 vector, $N$ is number of individuals, the columns are centered.
$\tilde{X}$: the genetic component of gene expression, $N$ x $J$ matrix, $J$ is number of genes, the columns are centered.
$G$: genotype (standardized). $N$ x $M$ matrix, $M$ is number of SNPs.

@@

We use the spike and slab prior for gene expression effect size $\beta_j$ (effect size for gene $j$).
$$\beta_j|\pi,\tau \sim (1- \pi_\beta)\delta_0 + \pi_\beta N(0, \sigma_\beta^2/\tau)$$
Here $\delta_0$ is point mass at 0 ($\delta_0(\beta_j)=1$ if $\beta_j=0$, otherwise $\delta_0(\beta_j)=0$ ).

We use the spike and slab prior for SNP effect size $\theta_m$ (effect size for SNP $m$).
$$ \theta_m | \tau \sim (1- \pi_\theta)\delta_0 + \pi_\theta N(0, \sigma_\theta^2/\tau)$$

>>>>

## Sparse model for expression and genotype
$$Y = \tilde{X}\beta + G\theta + \epsilon$$
$Y$: quantitative traits, $N$ x 1 vector, $N$ is number of individuals, the columns are centered.

$\tilde{X}$: the genetic component of gene expression, $N$ x $J$ matrix, $J$ is number of genes, the columns are centered.

$G$: genotype (standardized). $N$ x $M$ matrix, $M$ is number of SNPs.

@@

We use the spike and slab prior for gene expression effect size $\beta_j$ (effect size for gene $j$).
$$\beta_j|\pi_\beta,\tau \sim (1- \pi_\beta)\delta_0 + \pi_\beta N(0, \sigma_\beta^2/\tau)$$
Here $\delta_0$ is point mass at 0 ($\delta_0(\beta_j)=1$ if $\beta_j=0$, otherwise $\delta_0(\beta_j)=0$ ).

We use the spike and slab prior for SNP effect size $\theta_m$ (effect size for SNP $m$).
$$ \theta_m | \tau, \pi_\theta\sim (1- \pi_\theta)\delta_0 + \pi_\theta N(0, \sigma_\theta^2/\tau)$$
